---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# colorio

<!-- badges: start -->
[![R build status](https://github.com/ijlyttle/colorio/workflows/R-CMD-check/badge.svg)](https://github.com/ijlyttle/colorio/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of colorio is to provide low-level access to the [**colorio** Python package](https://github.com/nschloe/colorio), developed by Nico Schlömer; this package makes conversions between different color spaces and provides color-distance calculations. 
It includes some of the more-recent color spaces, such as [CAM02-UCS](https://en.wikipedia.org/wiki/CIECAM02), [CAM16-UCS](https://en.wikipedia.org/wiki/Color_appearance_model#CAM16), and [Jzazbz](https://doi.org/10.1364/OE.25.015131).

There's a lot to the colorio Python package; the goal of this README is to highlight those parts that concern conversion among color spaces, and distance calculations within a color space.

## Installation

You can install the development version of colorio from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ijlyttle/colorio")
```

Because this package uses the colorio Python package, you may need to follow a few steps. My recommendations are to 

- use (or create) a Conda installation. 
- use (or create) a Python environment called `r-reticulate`.
- install the colorio Python package.

```r
reticulate::install_miniconda()
reticulate::conda_create("r-reticulate")
colorio::install_colorio()
```

To confirm everything is working, you can call `check_colorio()`:

```{r}
colorio::check_colorio()
```

## Example

```{r example}
library("colorio")
## basic example code
```

In colorio, the basic unit of analysis is the color space. 
We will call functions that will create color-space objects; those objects will have methods we can call to convert to and from the "central" color-space: XYZ100, the [CIE 1931 XYZ color space](https://en.wikipedia.org/wiki/CIE_1931_color_space), normalized to 100.

To convert values from one color space to another, we create each of the color-space objects - then use the `to_xyz100()` method from one of the color spaces, then the `from_xyz100()`  method from the other.
